---
title: "Group 23"
author: "318356995 , 207133109 , 318359726"
date: "12/4/2021"
output: word_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fitdistrplus)
library(magrittr)
```


```{r 1, echo=FALSE}
filePath=choose.files() 
table<-read.csv(filePath,header=TRUE)
Data<-table[,1]
Data<-Data[1:50]
```

Checking the data, first impression:
```{r 2 , echo=FALSE}
par(mfrow=c(1,3)) # defines 2 plots on the same window
plot(Data,ylab="Sample values") # plot ( left graph )
hist(Data, ylab="Frequency ") # histogram (right graph)
boxplot(Data)
```


now, we will try estimating the parameters of a normal(mean and sd) & exponential(lambda) distribution. 
The fitting for exponential distribution will fail because we have impossible values - negatives.
```{r fitting norm}
normFit<-fitdist(Data,"norm") # fitting a normal distrbution 
summary(normFit) # summary function displays the results 
#expFit<-fitdist(Data,"exp") # fitting an expo distrbution 
#summary(expFit)
```


now we will show the graphs for normal distribution - Desnsity, CDF, QQ-Plot, PP-Plot
```{r}
plotdist(Data,"norm",para=list(mean=normFit$estimate[1], sd=normFit$estimate[2] ) )
```
now, we will check if the data is fitted from a normal distribution with estimate mean and sd that we got from the last chunk. by applying the K-S test, we will get:
```{r 5 ,echo=FALSE}
normgof<- gofstat(normFit)%>%print()
normgof$kstest%>%print()
```
from the output, we got:
"not rejected" H0. so we can say now that the data is fitted from a normal distribution.
